---
title: "kkd2-2 MCAOarticle, analysis using both flox and creflox samples"
output: html_notebook
---

# 0. Load libraries, basic own functions, and required parameters
```{r}
# Load libraries
library(Seurat)
library(DoubletFinder)
library(ggplot2)
library(tidyverse)
library(gtable)
library(grid)
library(ggstatsplot)
library(progress)
library(gridExtra)
library(VennDiagram)

# Basic own functions
## is all same
isallsame <- function(x, y) { all((x==y)==TRUE) }

## grep for all
grepall <- function(x, y) { unlist(lapply(x,grep,y)) }

## which for all
whichall <- function(x,y) {
  Out <- c()
  for(i in seq_along(x)) { Out <- c(Out, which(y==x[i])) }
  Out
}

# Parameters
SampleIDs <- c("N.flox","N.LMcreflox","MO1h.flox","MO1h.LMcreflox","MO3h.flox","MO3h.LMcreflox")
nSample <- length(SampleIDs)
```


# 1. Load RAW data
```{r}
# Make "each sample directory name" same as "SampleIDs"
data.list <- list()
for (i in 1:nSample) {
  data.list[i] <- Read10X(data.dir = paste("/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_082319/MCAOall_out", SampleIDs[i], "filtered_feature_bc_matrix", sep="/"))
  names(data.list)[i] <- SampleIDs[i]
}
print("Before equalize cell numbers")
unlist(lapply(data.list, ncol))
```


# 2. Remove Doublet
R package: DoubletFinder
https://github.com/chris-mcginnis-ucsf/DoubletFinder

Prepare Functions for doublet removal
```{r}
# Pre-process Seurat objects
Preprocess <- function(sample, nFeature.min, nFeature.max, percent.mt.max, dims.max, resolution) {
  sample2 <- subset(x = sample, cells = names(sample$nFeature_RNA)[which(sample$nFeature_RNA > nFeature.min)])
  sample2 <- subset(x = sample2, cells = names(sample$nFeature_RNA)[which(sample$nFeature_RNA < nFeature.max)])
  sample2 <- subset(x = sample2, cells = names(sample$percent.mt)[which(sample$percent.mt < percent.mt.max)])
  sample2 <- FindVariableFeatures(object = sample2, selection.method = "vst", nfeatures = 2000)
  sample2 <- ScaleData(object = sample2)
  sample2 <- RunPCA(sample2)
  sample2 <- FindNeighbors(object = sample2, dims = 1:dims.max)
  sample2 <- FindClusters(object = sample2, resolution = resolution)
  sample2 <- RunUMAP(sample2, dims = 1:dims.max)
  return(sample2)
}

# Find Doublet
FindDoublet <- function(sample, dims.max, AssumeDoublet, pN, pK) {
  ## Homotypic Doublet Proportion Estimate
  homotypic.prop <- modelHomotypic(sample@active.ident) ## ex: annotations <- seu_test@meta.data$ClusteringResults
  nExp_poi <- round(AssumeDoublet*length(sample@active.ident))  
  nExp_poi.adj <- round(nExp_poi*(1-homotypic.prop))
  
  ## Run DoubletFinder with varying classification stringencies
  sample2 <- doubletFinder_v3(sample, PCs = 1:dims.max, pN = pN, pK = pK, nExp = nExp_poi.adj, reuse.pANN = FALSE, sct = FALSE)
  return(sample2)
}

# Remove doublet
RemoveDoublet <- function(sample) {
  DF.position <- grep("DF.classifications",colnames(sample@meta.data))
  if (length(DF.position) == 1) {
    DF.classifications <- sample@meta.data[DF.position]
    Singlet.ID <- rownames(DF.classifications)[which(DF.classifications=="Singlet")]
    sample2 <- subset(sample, cells=Singlet.ID)
    return(sample2)
  } 
  else { (print("ERROR: multiple DF.classifications")) }
}
```

Remove Doublet
## DR-1 Pre-process Seurat object
```{r}
# Create and Normalize Seurat.object
Seurat.list <- data.list %>% lapply(CreateSeuratObject, min.cells = 3, min.features = 200) %>% lapply(NormalizeData)

# Check MT percentage and nFeature
nFeature.data <- data.frame(Sample=NA,Data=NA,stringsAsFactors = F)
perMT.data <- data.frame(Sample=NA,Data=NA,stringsAsFactors = F)
for (i in seq_along(Seurat.list)) {
  Seurat.list[[i]][["percent.mt"]] <- PercentageFeatureSet(object = Seurat.list[[i]], pattern = "^mt-")
  Seurat.list[[i]]$stim <- SampleIDs[i]
  nFeature.data <- rbind(nFeature.data, data.frame(Sample=names(Seurat.list)[[i]], Data=Seurat.list[[i]]$nFeature_RNA))
  perMT.data <- rbind(perMT.data, data.frame(Sample=names(Seurat.list)[[i]], Data=Seurat.list[[i]]$percent.mt))
}
nFeature.data <- na.omit(nFeature.data)
perMT.data <- na.omit(perMT.data)

# Check
ggplot(data=nFeature.data, aes(x=Sample,y=Data)) + geom_jitter(size=0.1) + scale_x_discrete(limit=SampleIDs)
ggplot(data=perMT.data, aes(x=Sample,y=Data)) + geom_jitter(size=0.1) + ylim(0,30)

# Pre-process Seurat objects
Seurat.list <- lapply(Seurat.list, Preprocess, nFeature.min=200, nFeature.max=6000, percent.mt.max=10, dims.max=15, resolution=0.5)
Elbow.list <- lapply(Seurat.list, ElbowPlot)
for (i in seq_along(Elbow.list)) { plot(Elbow.list[[i]]) }
```

## DR-2 Find and Remove doublet
```{r}
## Assuming 7.6% doublet formation rate - 10X genomics, loading 16,000 cells
Seurat.list <- lapply(Seurat.list, FindDoublet, dims.max=15, AssumeDoublet=0.076, pN=0.25, pK=0.01)

# Percentage of detected doublets 
for (i in seq_along(Seurat.list)) {
  DF.position <- grep("DF.classifications", colnames(Seurat.list[[i]]@meta.data))
  print(names(Seurat.list)[i])
  print(length(which(Seurat.list[[i]]@meta.data[DF.position]=="Doublet"))*100/ncol(Seurat.list[[i]]))
}
# Visualization of doublets
for (i in seq_along(Seurat.list)) {
  DF.position <- grep("DF.classifications", colnames(Seurat.list[[i]]@meta.data))
  names(Seurat.list[[i]]@meta.data)[DF.position] <- "DF.classifications"
  plot(DimPlot(object = Seurat.list[[i]], reduction = "umap", label=T, label.size=5, group.by = "DF.classifications"))
}

# Remove doublets
Seurat.list2 <- lapply(Seurat.list, RemoveDoublet)
```


# 3. Equalize cell number
```{r}
# Equalize the cell number among each sample
# **Choose the first 7156 cells in this case**
print("Before equalize cell numbers")
unlist(lapply(Seurat.list2, ncol))

nMin <- min(unlist(lapply(Seurat.list2, ncol)))
Seurat.list2 <- lapply(Seurat.list2, function(x) { x[,1:nMin] }) # Choose the cells in first "nMin" column 
print("After equalize cell numbers")
unlist(lapply(Seurat.list2, ncol))
```


# 4. Merge Seurat object and Clusterize the data
```{r}
# Merge all Seurat object
MCAOall <- merge(x=Seurat.list2[[1]], y=Seurat.list2[-1])
# [Identification of highly variable features (feature selection)]
MCAOall <- FindVariableFeatures(object = MCAOall, selection.method = "vst", nfeatures = 2000)
```

```{r}
# Select meta.data
MCAOall@meta.data = MCAOall@meta.data %>% select(-pANN_0.25_0.01_447,-DF.classifications,-pANN_0.25_0.01_452,-pANN_0.25_0.01_548,-pANN_0.25_0.01_663,-pANN_0.25_0.01_483,-pANN_0.25_0.01_713)

# [Scaling the data] =Z-score??
all.genes <- rownames(x = MCAOall)
MCAOall <- ScaleData(object = MCAOall, features=all.genes)
rm(all.genes)

# [Perform linear dimensional reduction]
MCAOall <- RunPCA(object = MCAOall, features = VariableFeatures(object = MCAOall))

# Examine and visualize PCA results a few different ways
DimPlot(object = MCAOall, reduction = "pca")
ElbowPlot(object = MCAOall)

# [Cluster the cells]
MCAOall <- FindNeighbors(object = MCAOall, dims = 1:20)
MCAOall <- FindClusters(object = MCAOall, resolution = 0.5)
MCAOall <- RunUMAP(object = MCAOall, dims = 1:20)
```


# 5. Find Markers and name cell types
```{r}
if (0) {
# [Finding differentially expressed features (cluster biomarkers)]
# find markers for every cluster compared to all remaining cells, report only the positive ones
library(plyr)
library(dplyr)
library(Matrix)

MCAOall.markers <- FindAllMarkers(object = MCAOall, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
MCAOall.markers %>% group_by(cluster) %>% top_n(n = 2, wt = avg_logFC)
write.csv(MCAOall.markers, file="MCAO.all.markers.csv")
}
```

Cluster	Cell_type	Marker_gene
0	MG1	Cx3cr1, Tmem119
1	MG5	Cx3cr1, Tmem119
2	MG8	Cx3cr1, Tmem119
3	MG6	Cx3cr1, Tmem119
4	MG7	Cx3cr1, Tmem119
5	Neut2	S100a8, Mmp8, Mmp9, Ly6g
6	MG4	Cx3cr1, Tmem119
7	Ly6ChiMo	Ccr2, Ly6c2
8	Tcell	Cd3d, Cd3g
9	Bcell	Igkc, Cd79a, Cd79b
10	MP-DC	Ccr2, H2-Ab1, Mrc1, Flt3
11	resMo	Fcgr4, Ear2
12	Neut1	S100a8, Mmp8, Mmp9, Ly6g
13	NK	Gzma, Gzmb, Prf1, Klrk1
14	MG2	Cx3cr1, Tmem119
15	Prolif	Mki67, Ccr2, Ly6c2
16	MG3	Cx3cr1, Tmem119
17	Others	Neut?

**dims=20**  **resolution=0.6**
```{r}
# Name cell types
new.cluster.ids <- c("MG1","MG5","MG8","MG6","MG7","Neut2","MG4","Ly6ChiMo","Tcell","Bcell","MP-DC","resMo","Neut1","NK","MG2","Prolif","MG3","Others")
names(x = new.cluster.ids) <- levels(x = MCAOall)
MCAOall <- RenameIdents(object = MCAOall, new.cluster.ids)
rm(new.cluster.ids)

# Change the order of cell types
Idents(object = MCAOall) <- factor(x = Idents(object = MCAOall), levels = c("MG1","MG2","MG3","MG4","MG5","MG6","MG7","MG8","Neut1","Neut2","Ly6ChiMo","resMo","MP-DC","Tcell","NK","Bcell","Prolif","Others"))
```

```{r}
DimPlot(MCAOall, reduction = "umap", label=T, label.size =5)
```

# 6. Add metadata
```{r}
MCAOall$orig.celltype <- MCAOall@active.ident
MCAOall$timepoint <- MCAOall$stim %>% replace(grep("N.", MCAOall$stim),"0h") %>% replace(grep("MO1h.", MCAOall$stim),"1h") %>% replace(grep("MO3h.", MCAOall$stim),"3h")
MCAOall$strain <- MCAOall$stim %>% replace(c(grep("N.flox",.),grep("h.flox", .)),"flox") %>% replace(grep(".LMcreflox",.), "LMcreflox")
```

```{r}
saveRDS(MCAOall, "/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_121819/MCAOall_121819.rds")
```


# 7. Reçlustering proliferating cells
```{r}
Prolif <- subset(MCAOall, idents="Prolif")
Prolif <- FindVariableFeatures(object = Prolif, selection.method = "vst", nfeatures = 2000)
Prolif <- RunPCA(object = Prolif, features = VariableFeatures(object = Prolif))
ElbowPlot(object = Prolif)
Prolif <- FindNeighbors(object = Prolif, dims = 1:10)
Prolif <- FindClusters(object = Prolif, resolution = 0.1)
Prolif <- RunUMAP(Prolif, reduction = "pca", dims = 1:10)
DimPlot(Prolif, reduction = "umap", label=T, label.size =5)
FeaturePlot(object = Prolif, features = c("Ly6c2","Itgam","Cd3d"), cols = c("lightgrey", "red"))

# Itgam_Ly6c2_posi cells: idents=c("0","1")
# Cd3_posi cells: idents=c("3")
```

# 8. Reclustering MP-DC
```{r}
MPDC <- subset(MCAOall, idents="MP-DC")
MPDC <- FindVariableFeatures(object = MPDC, selection.method = "vst", nfeatures = 2000)
MPDC <- RunPCA(object = MPDC, features = VariableFeatures(object = MPDC))
ElbowPlot(object = MPDC)
MPDC <- FindNeighbors(object = MPDC, dims = 1:10)
MPDC <- FindClusters(object = MPDC, resolution = 0.1)
MPDC <- RunUMAP(MPDC, reduction = "pca", dims = 1:10)
DimPlot(MPDC, reduction = "umap", label=T, label.size =5)
FeaturePlot(object = MPDC, features = c("Mrc1","Itgax","Flt3"), cols = c("lightgrey", "red"))

# Mrc1_posi cells: idents=c("0") → MP
# Itgax_Flt3_posi cells: idents=c("1","2") → DC  ("2": Itgam_nega cDC?)
```

# 9. Re-define cells
Prolif_Cd11b(Itgam)+ Ly6C(Ly6c2)+ : Ly6ChiMo_prolif
Prolif_Cd3+ : Tcell_prolif

```{r}
Prolif_Itgam_Ly6c2_posi_ID <- WhichCells(Prolif, idents = c("0","1"))
Prolif_Cd3_posi_ID <- WhichCells(Prolif, idents = "3")

MPDC_Mrc1_posi_ID <- WhichCells(MPDC, idents = "0")
MODC_Itgax_Flt3_posi_ID <- WhichCells(MPDC, idents = c("1","2"))

MCAOall$final.celltype = as.character(MCAOall$orig.celltype) %>% replace(grep("^Prolif", MCAOall$orig.celltype), "Others_prolif")
MCAOall$final.celltype = MCAOall$final.celltype %>% replace(whichall(Prolif_Itgam_Ly6c2_posi_ID, names(MCAOall$orig.celltype)), "Ly6ChiMo_prolif")
MCAOall$final.celltype = MCAOall$final.celltype %>% replace(whichall(Prolif_Cd3_posi_ID, names(MCAOall$orig.celltype)), "Tcell_prolif")
MCAOall$final.celltype = MCAOall$final.celltype %>% replace(whichall(MPDC_Mrc1_posi_ID, names(MCAOall$orig.celltype)), "MP")
MCAOall$final.celltype = MCAOall$final.celltype %>% replace(whichall(MODC_Itgax_Flt3_posi_ID, names(MCAOall$orig.celltype)), "DC")
MCAOall$final.celltype = MCAOall$final.celltype %>% replace(grep("^MG", MCAOall$orig.celltype), "Microglia")
MCAOall$final.celltype = MCAOall$final.celltype %>% replace(grep("^Neut", MCAOall$orig.celltype), "Neut")
MCAOall$final.celltype %>% unique

Idents(MCAOall) <- MCAOall$final.celltype
```

```{r}
order <- c("Microglia","MP","DC","Ly6ChiMo","Ly6ChiMo_prolif","resMo","Neut","Tcell","Tcell_prolif","Bcell","NK","Others","Others_prolif")
DimPlot(object = MCAOall, reduction = "umap",  order=rev(order), label=T, label.size=3) 
```

```{r}
saveRDS(MCAOall, "/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_121819/MCAOall_121819_finalcelltype.rds")
```

```{r}
MCAOall <- readRDS("/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_121819/MCAOall_121819_finalcelltype.rds")
```





# 10. Find Markers of "final.celltype"
```{r}
# [Finding differentially expressed features (cluster biomarkers)]
# find markers for every cluster compared to all remaining cells, report only the positive ones
library(plyr)
library(dplyr)
library(Matrix)

Idents(MCAOall) <- MCAOall$final.celltype
MCAOall.finalcelltype.markers <- FindAllMarkers(object = MCAOall, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
MCAOall.finalcelltype.markers %>% group_by(cluster) %>% top_n(n = 2, wt = avg_logFC)
write.csv(MCAOall.finalcelltype.markers, file="/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_121819/MCAOall.finalcelltype.markers.csv")
```

# 11. Visualize Markers of "final.celltype"

Top 5 markers
```{r}
MCAOall.finalcelltype.markers <- read.csv("/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_121819/MCAOall.finalcelltype.markers.csv", header = T, stringsAsFactors = F)
MCAOall.finalcelltype.markers %>% group_by(cluster) %>% top_n(n = 5, wt = avg_logFC)
```


Visualization
```{r}
Markers <- read.csv("/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_121819/MCAOall_markers_forPlot3.csv", header=T, stringsAsFactors = F)

features <- c()
for(i in seq_along(colnames(Markers))) {
  features <- c(features, Markers[,i])
}
features <- unique(features[-which(features=="")])

order <- c("Microglia","MP","DC","Ly6ChiMo","Ly6ChiMo_prolif","resMo","Neut","Tcell","Bcell","NK")

DotPlot(
  MCAOall,
  assay = NULL,
  features = features,
  cols = c("lightgrey", "blue"),
  col.min = -2.5,
  col.max = 2.5,
  dot.min = 0,
  dot.scale = 6,
  group.by = NULL,
  split.by = NULL,
  scale.by = "radius",
  scale.min = NA,
  scale.max = NA
) + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + scale_y_discrete(limits=order) + coord_flip()
```

# 12. Identify Cd300a-knocked down celltypes by Lyz2-cre = causal celltype for the MCAO phenotype

Detection of DEGs for each Celltype: KOvsWT
```{r}
if (isallsame(names(MCAOall$strain), names(MCAOall$final.celltype))) {
  MCAOall$strain_final.celltype <- paste(MCAOall$strain, MCAOall$final.celltype, sep="_")
} else { print("vector orders are not same") } 
  
Idents(MCAOall) <- MCAOall$strain_final.celltype
MCAOall.KOvsWT.list <- vector("list", length=length(unique(MCAOall$final.celltype)))

pb <- progress_bar$new(total = length(unique(MCAOall$final.celltype)), format="[:bar] :percent 経過 :elapsed 終了まで: :eta", clear=TRUE)
for (i in seq_along(unique(MCAOall$final.celltype))) {
  pb$tick()
  
  ident.1 <- paste0("LMcreflox_", unique(MCAOall$final.celltype)[i])
  ident.2 <- paste0("flox_", unique(MCAOall$final.celltype)[i])
  length.1 <- length(which(MCAOall$strain_final.celltype==ident.1))
  length.2 <- length(which(MCAOall$strain_final.celltype==ident.2))
  
  if(length.1>=3 && length.2>=3) {
    MCAOall.KOvsWT.list[[i]] <- suppressWarnings(FindMarkers(object = MCAOall, ident.1 = ident.1, ident.2 = ident.2, verbose = FALSE))
    names(MCAOall.KOvsWT.list)[i] <- unique(MCAOall$final.celltype)[i]
  } else { print(paste0(unique(MCAOall$final.celltype)[i], " didn't have enough cells")) }
  
  rm(list=c("ident.1","ident.2","length.1","length.2")) 
  Sys.sleep(1 / length(unique(MCAOall$final.celltype)))
}
rm(pb)

Idents(MCAOall) <- MCAOall$final.celltype
```

Detect Cd300a-knocked down celltypes by Lyz2-cre
```{r}
# Choose list for analysis
KOvsWT.list <- MCAOall.KOvsWT.list

Cd300a.dif.celltype <- c()
for (i in 1:length(KOvsWT.list)) {
  if (is.element("Cd300a", rownames(KOvsWT.list[[i]])) && (KOvsWT.list[[i]]["Cd300a","p_val_adj"]<0.05)) {
    print(unlist(c(names(KOvsWT.list)[i], KOvsWT.list[[i]]["Cd300a",c("avg_logFC","p_val","p_val_adj")])))
    Cd300a.dif.celltype <- c(Cd300a.dif.celltype, names(KOvsWT.list)[i])
  } else {}
}  
```

Visualization
```{r}
gene <- "Cd300a"
cell.sample <- c("Microglia","MP","DC","Ly6ChiMo","Ly6ChiMo_prolif","resMo","Neut","Tcell","Tcell_prolif","Bcell","NK","Others","Others_prolif")
group <- "strain"
plot.list <- list()

for (i in seq_along(cell.sample)) {
plot.list[[i]] <- VlnPlot(MCAOall, idents = cell.sample[i], features = gene, group.by = group, pt.size=0, slot="data", cols=c("white", "grey")) + ylab("Expression") + stat_summary(fun.y = mean, geom='point', size = 10, colour = "black", shape=95) + theme(legend.position="none", axis.title.x = element_blank(), axis.text.x=element_blank(), axis.title.y = element_blank(), plot.title=element_text(size=13, face="plain")) + ggtitle(paste(cell.sample[i]))

# + ggtitle(paste(cell.sample[i]))  plot.title=element_text(size=25, face="plain")
}

do.call(gridExtra::grid.arrange, c(plot.list, nrow = 2))
rm(list=c("cell.sample","plot.list","gene","group"))
```

# 13. Combine Ly6ChiMo and Ly6ChiMo_prolif
```{r}
MCAOall$final.celltype_forScoring = MCAOall$final.celltype %>% replace(grep("^Ly6ChiMo", MCAOall$final.celltype), "Ly6ChiMo_all")
MCAOall$final.celltype_forScoring = MCAOall$final.celltype_forScoring %>% replace(grep("^Tcell", MCAOall$final.celltype), "Tcell_all")

MCAOall$final.celltype_forScoring %>% unique

Idents(MCAOall) <- MCAOall$final.celltype_forScoring
DimPlot(object = MCAOall, reduction = "umap",  order=rev(levels(Idents(MCAOall))), label=T, label.size=3) 
```

```{r}
FeaturePlot(MCAOall, features=c("Lyz2","Itgam"))
```




# 14. Scoring for cell phenotype

## 14-1. Load gene expression data after several stimulation

### Efferocytosis data
GSE1197273
Nature, 563:714, 2019. Efferocytosis induces a novel SLC program to promote glucose uptake and lactate release.

### Other MP activation data: LPS, Ifng, and Ifnb stimulation
GSE44292
J Leukoc Biol, 96:167, 2014. Analysis of the transcriptional networks underpinning the activation of murine macrophages by inflammatory mediators.

```{r}
# Efferocytosis data
Efferocytosis.data <- read.csv("/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_082319/GSE119273_Phago+AC_bulkRNA/GSE119273_LR73_AC_padj-notNA.csv", header = T, stringsAsFactors = F)

head(Efferocytosis.data, n=10)
```

```{r}
# Other MP activation data
MP_LPS.data <- read.csv("/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_082319/MP-stim_transcriptome/GSE44292_MP/GSE44292_MP-LPS-4h.csv", header=T, stringsAsFactors = F)
MP_Ifng.data <- read.csv("/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_082319/MP-stim_transcriptome/GSE44292_MP/GSE44292_MP-Ifng-4h.csv", header=T, stringsAsFactors = F)
MP_Ifnb.data <- read.csv("/Users/kazumasa/Desktop/Single cell RNAseq/Work_oriData/MCAOall_082319/MP-stim_transcriptome/GSE44292_MP/GSE44292_MP-Ifnb-4h.csv", header=T, stringsAsFactors = F)

head(MP_LPS.data, n=20)
```

## 14-2. Define UP and DOWN genes based on each data
```{r}
p_threshold <- 0.05

# Efferocytosis
## padj < 0.05, UP in Phago+AC & Exist in MCAO samples
Effero.UP <- subset(Efferocytosis.data, Efferocytosis.data$padj <= p_threshold & Efferocytosis.data$log2FoldChange > 0)$gene
Effero.UP <- intersect(rownames(MCAOall), Effero.UP)
## padj < 0.05, DOWN in Phago+AC & Exist in MCAO samples
Effero.DOWN <- subset(Efferocytosis.data, Efferocytosis.data$padj <= p_threshold & Efferocytosis.data$log2FoldChange < 0)$gene
Effero.DOWN <- intersect(rownames(MCAOall), Effero.DOWN)

# LPS
## padj < 0.05, UP after LPS & Exist in MCAO samples
LPS.UP <- subset(MP_LPS.data, MP_LPS.data$adj.P.Val <= p_threshold & MP_LPS.data$logFC > 0)$Gene.symbol
LPS.UP <- intersect(rownames(MCAOall), LPS.UP)
## padj < 0.05, DOWN after LPS & Exist in MCAO samples
LPS.DOWN <- subset(MP_LPS.data, MP_LPS.data$adj.P.Val <= p_threshold & MP_LPS.data$logFC < 0)$Gene.symbol
LPS.DOWN <- intersect(rownames(MCAOall), LPS.DOWN)

# Ifng
## padj < 0.05, UP after LPS & Exist in MCAO samples
Ifng.UP <- subset(MP_Ifng.data, MP_Ifng.data$adj.P.Val <= p_threshold & MP_Ifng.data$logFC > 0)$Gene.symbol
Ifng.UP <- intersect(rownames(MCAOall), Ifng.UP)
## padj < 0.05, DOWN after Ifng & Exist in MCAO samples
Ifng.DOWN <- subset(MP_Ifng.data, MP_Ifng.data$adj.P.Val <= p_threshold & MP_Ifng.data$logFC < 0)$Gene.symbol
Ifng.DOWN <- intersect(rownames(MCAOall), Ifng.DOWN)

# Ifnb
## padj < 0.05, UP after LPS & Exist in MCAO samples
Ifnb.UP <- subset(MP_Ifnb.data, MP_Ifnb.data$adj.P.Val <= p_threshold & MP_Ifnb.data$logFC > 0)$Gene.symbol
Ifnb.UP <- intersect(rownames(MCAOall), Ifnb.UP)
## padj < 0.05, DOWN after Ifnb & Exist in MCAO samples
Ifnb.DOWN <- subset(MP_Ifnb.data, MP_Ifnb.data$adj.P.Val <= p_threshold & MP_Ifnb.data$logFC < 0)$Gene.symbol
Ifnb.DOWN <- intersect(rownames(MCAOall), Ifnb.DOWN)
```

## 14-3. Prepare scoring function 
・UP score (UP0.1.int genes): (Calculate (**MCAO1h - mean(Naive)**) for each gene (only *more* than 0) and take sum) / each cell
・DOWN score (DOWN0.1.int genes): *-*(Calculate (**MCAO1h - mean(Naive)**) for each gene (only *less* than 0) and take sum) / each cell
・Total score: UP score + DOWN score

```{r}
Scoring_strains <- function(
  ObjectForScoring,
  IdentsForScoring,  # Select from ObjectForScoring@meta.data %>% colnames()
  CellsForScoring,
  TimeForScoring,  # Select from ObjectForScoring$timepoint : "0h" or "1h" or "3h"
  UPgenes,
  DOWNgenes,
  Name,
  ymin,
  ymax,
  Strains = c("flox","LMcreflox")
) {
  
  # functions
  SubstractNaive <- function(x) { x-Naive.mean } 
  reROWnames <- function(x, replace) { rownames(x)<-replace; x } # Put 2 orders in one line → ;
  MergeUPDOWN <- function(x) {
    Out <- vector("list", length=length(x))
    names(Out) <- names(x)
    for (i in seq_along(x)) {
      UPscore <- apply(x[[i]][["UP"]]*(x[[i]][["UP"]]>0), MARGIN = 2, sum) 
      DOWNscore <- -(apply(x[[i]][["DOWN"]]*(x[[i]][["DOWN"]]<0), MARGIN = 2, sum)) # Take inverse number for DOWNscore 
      Out[[i]] <- UPscore + DOWNscore
      rm(list=c("UPscore", "DOWNscore"))
     }
    Out2 <- data.frame(Strain=rep("flox", length=length(Out[["flox"]])), Score=Out[["flox"]])
    Out2 <- rbind(Out2, data.frame(Strain=rep("LMcreflox", length=length(Out[["LMcreflox"]])), Score=Out[["LMcreflox"]]))
    Out2
  }
  
  # Differential list (Dif.list $ Celltype $ Strain $ UP or DOWN) 
  Dif.list <- vector("list", length=length(CellsForScoring))
  names(Dif.list) <- CellsForScoring
  
  for (i in seq_along(CellsForScoring)) {  # for each celltype
    Dif.list[[i]] <- vector("list",length=2)
    names(Dif.list[[i]]) <- Strains
  
    for (j in seq_along(Strains)) {
      Dif.list[[i]][[j]] <- vector("list",length=2)
      names(Dif.list[[i]][[j]]) <- c("UP", "DOWN")
      
      Naive.CellIDs = ObjectForScoring@meta.data %>% rownames_to_column(var="CellID") %>% .[whichall(CellsForScoring[i], ObjectForScoring@meta.data[,grep(IdentsForScoring, colnames(ObjectForScoring@meta.data))]),] %>% filter(timepoint=="0h" & strain==Strains[j]) %>% pull(CellID)
      Treat.CellIDs = ObjectForScoring@meta.data %>% rownames_to_column(var="CellID") %>% .[whichall(CellsForScoring[i], ObjectForScoring@meta.data[,grep(IdentsForScoring, colnames(ObjectForScoring@meta.data))]),] %>% filter(timepoint==TimeForScoring & strain==Strains[j]) %>% pull(CellID)
      
      # Calculation for UP genes
      Naive.mean <- ObjectForScoring@assays$RNA@scale.data[UPgenes, Naive.CellIDs] %>% apply(MARGIN = 1, mean) %>% matrix(ncol=1, nrow=length(UPgenes))
      Dif.list[[i]][[j]][["UP"]] <- ObjectForScoring@assays$RNA@scale.data[UPgenes, Treat.CellIDs] %>% apply(MARGIN = 2, SubstractNaive) %>% reROWnames(.,replace=UPgenes)
      rm(Naive.mean)
      
      # Calculation for DOWN genes
      Naive.mean <- ObjectForScoring@assays$RNA@scale.data[DOWNgenes, Naive.CellIDs] %>% apply(MARGIN = 1, mean) %>% matrix(ncol=1, nrow=length(DOWNgenes))
      Dif.list[[i]][[j]][["DOWN"]] <- ObjectForScoring@assays$RNA@scale.data[DOWNgenes, Treat.CellIDs] %>% apply(MARGIN = 2, SubstractNaive) %>% reROWnames(.,replace=DOWNgenes)
      rm(list=c("Naive.mean","Naive.CellIDs","Treat.CellIDs"))
    }
  }
  
  Sco.list <- lapply(Dif.list, MergeUPDOWN)
  
  plot.list <- vector("list", length=length(CellsForScoring))
  for (i in seq_along(CellsForScoring)) {
  plot.list[[i]] <- ggplot(Sco.list[[i]], aes(x=Strain, y=Score)) +ggtitle(CellsForScoring[i]) + geom_violin() +    theme(legend.position="none", axis.title.x = element_blank(), title =element_text(size=13, face='bold'), axis.title.y = element_text(size=14, face='plain'), axis.text.x = element_text(size=14, angle = 45, hjust = 1)) + geom_jitter(shape=16, size=NA) + stat_summary(fun.y = mean, geom='point', size = 15, colour = "red", shape=95)  + theme_classic() + ylim(ymin, ymax)
  }

  return1 <- do.call("grid.arrange", c(plot.list, nrow = 1, top = Name))
                     
  wilcox.list <- vector("list", length=length(CellsForScoring))
  for (i in seq_along(CellsForScoring)) {
    x <- subset(Sco.list[[i]], subset=Sco.list[[i]]$Strain=="flox")$Score
    y <- subset(Sco.list[[i]], subset=Sco.list[[i]]$Strain=="LMcreflox")$Score
    wilcox.list[[i]] <- exactRankTests::wilcox.exact(x=x,y=y,paired=F)
    names(wilcox.list)[i] <- CellsForScoring[i]
    rm(list=c("x","y"))
  }
  
  return2 <- print(wilcox.list)
  return(list(return1, return2))
  
}
```


## 14-4. Calculate each score

Efferocytosis
```{r}
Scoring_strains(
  ObjectForScoring = MCAOall, 
  IdentsForScoring = "final.celltype_forScoring", 
  CellsForScoring = c("resMo","Ly6ChiMo_all","MP","Neut"),
  TimeForScoring = "1h",  # Select from ObjectForScoring$timepoint : "0h" or "1h" or "3h"
  UPgenes = Effero.UP,
  DOWNgenes = Effero.DOWN,
  Name = "Efferocytosis",
  ymin = 100,
  ymax = 800
)
```

```{r}
Scoring_strains(
  ObjectForScoring = MCAOall, 
  IdentsForScoring = "final.celltype", 
  CellsForScoring = c("Ly6ChiMo","Ly6ChiMo_prolif"),
  TimeForScoring = "1h",  # Select from ObjectForScoring$timepoint : "0h" or "1h" or "3h"
  UPgenes = Effero.UP,
  DOWNgenes = Effero.DOWN,
  Name = "Efferocytosis",
  ymin = 100,
  ymax = 800
)
```


LPS stimulation
```{r}
Scoring_strains(
  ObjectForScoring = MCAOall, 
  IdentsForScoring = "final.celltype_forScoring", 
  CellsForScoring = c("resMo","Ly6ChiMo_all","MP","Neut"),
  TimeForScoring = "1h",  # Select from ObjectForScoring$timepoint : "0h" or "1h" or "3h"
  UPgenes = LPS.UP,
  DOWNgenes = LPS.DOWN,
  Name = "LPS stimulation",
  ymin = 100,
  ymax = 600
)
```

IFNg stimulation
```{r}
Scoring_strains(
  ObjectForScoring = MCAOall, 
  IdentsForScoring = "final.celltype_forScoring", 
  CellsForScoring = c("resMo","Ly6ChiMo_all","MP","Neut"),
  TimeForScoring = "1h",  # Select from ObjectForScoring$timepoint : "0h" or "1h" or "3h"
  UPgenes = Ifng.UP,
  DOWNgenes = Ifng.DOWN,
  Name = "Ifng stimulation",
  ymin = 0,
  ymax = 550
)
```

IFNb stimulation
```{r}
Scoring_strains(
  ObjectForScoring = MCAOall, 
  IdentsForScoring = "final.celltype_forScoring", 
  CellsForScoring = c("resMo","Ly6ChiMo_all","MP","Neut"),
  TimeForScoring = "1h",  # Select from ObjectForScoring$timepoint : "0h" or "1h" or "3h"
  UPgenes = Ifnb.UP,
  DOWNgenes = Ifnb.DOWN,
  Name = "Ifnb stimulation",
  ymin = 500,
  ymax = 2000
)
```


## 14-5. Common genes between Effero.UP genes and Ly6ChiMo-DEGs (KO vs WT at MCAO-1h)

### Prepare parameters
```{r}
if (isallsame(names(MCAOall$strain), names(MCAOall$final.celltype_forScoring))) {
  MCAOall$strain_final.celltype_forScoring <- paste(MCAOall$strain, MCAOall$final.celltype_forScoring, sep="_")
} else { print("Order of vectors are not same") }

if (isallsame(names(MCAOall$timepoint), names(MCAOall$strain_final.celltype_forScoring))) {
  MCAOall$timepoint_strain_final.celltype_forScoring <- paste(MCAOall$timepoint, MCAOall$strain_final.celltype_forScoring, sep="_")
} else { print("Order of vectors are not same") }

MCAOall$timepoint_strain_final.celltype_forScoring %>% unique()
```

### DEGs in Ly6ChiMo: KO vs WT (MCAO-1h)
```{r}
Idents(MCAOall) <- MCAOall$timepoint_strain_final.celltype_forScoring
Ly6ChiMo_1h_DEGs <- FindMarkers(MCAOall, ident.1 = "1h_LMcreflox_Ly6ChiMo_all", ident.2 = "1h_flox_Ly6ChiMo_all")
Ly6ChiMo_1h_UPinKO <- Ly6ChiMo_1h_DEGs %>% rownames_to_column(var="Gene") %>% filter(p_val_adj<=0.05) %>% filter(avg_logFC>0) %>% pull(Gene)
Idents(MCAOall) <- MCAOall$final.celltype_forScoring

Ly6ChiMo_1h_UPinKO
```

### Venn diagram of Effero.UP genes and Ly6ChiMo-1h-KOvsWT
```{r}
EfferoUP_DEGs_list <- list(EfferoUP=Effero.UP, DEGs=Ly6ChiMo_1h_UPinKO)
venn.diagram(EfferoUP_DEGs_list, filename="/Users/kazumasa/Desktop/Dry_analysis/kkd2_MCAOanalysis_forArticle/EfferoUP_DEGs_venn.jpg")
```


### Common genes of Effero.UP and Ly6ChiMo_1h_UPinKO
```{r}
intersect_genes <- intersect(Effero.UP, Ly6ChiMo_1h_UPinKO) 
intersect_genes
```

### Heatmap of common genes of Effero.UP and Ly6ChiMo_1h_UPinKO
```{r}
# After PANTHER analysis of intersect_gene
cellcyle_gene <- read.table("/Users/kazumasa/Desktop/Dry_analysis/kkd2_MCAOanalysis_forArticle/Intersected gene PANTHER/cellcycle.txt", header=F, sep="\t", quote = "", stringsAsFactors = F) %>% pull(V2)
cytoskeleton_organization_gene <- read.table("/Users/kazumasa/Desktop/Dry_analysis/kkd2_MCAOanalysis_forArticle/Intersected gene PANTHER/cytoskeleton organization.txt", header=F, sep="\t", quote = "", stringsAsFactors = F) %>% pull(V2)
```

```{r}
A <- setdiff(cellcyle_gene, intersect(cellcyle_gene, cytoskeleton_organization_gene))
B <- intersect(cellcyle_gene, cytoskeleton_organization_gene)
C <- setdiff(cytoskeleton_organization_gene, intersect(cellcyle_gene, cytoskeleton_organization_gene))
D <- setdiff(intersect_genes, c(A,B,C))
features <- c(A, B, C, D)
rm(list=c("A","B","C","D"))

Idents(MCAOall) <- MCAOall$timepoint_strain_final.celltype_forScoring
DoHeatmap(MCAOall, cells = WhichCells(MCAOall, idents = c("1h_flox_Ly6ChiMo_all","1h_LMcreflox_Ly6ChiMo_all")), features = features, draw.line=F) + NoLegend() + scale_fill_gradientn(colors = c("skyblue","white","red")) + theme(axis.text.y = element_text(size=15, face="plain"))
Idents(MCAOall) <- MCAOall$final.celltype_forScoring

clipr::write_clip(intersect_genes)
```



# 15. Cd300a and Cd300b expression in each time point
## 15-1. Prepare function
```{r}
# Combine metadata
Combine_metadata <- function(metadata1, metadata2){
  isallsame <- function(x, y) { all((x==y)==TRUE) }
  if(all((names(metadata1)==names(metadata2))==TRUE)){
    out <- paste(metadata1, metadata2, sep="_")
  } else {
    out <- stop("names (content of order) of two metadata are not same")
  }
  
  # as factor
  level <- expand.grid(levels(metadata1), levels(metadata2)) %>% apply(MARGIN = 1, function(x){paste(x[1],x[2],sep="_")})
  out <- factor(out, levels = level)
  return(out)
}


# VlnPlot with statistical analysis
## Modified 'VlnPlot' function
## Statistical analysis is using package "stats"
## stats::pairwise.wilcox.test

VlnPlot_with_stats <- function(object, 
                               cells, 
                               feature, 
                               xaxis = levels(object$sample), 
                               pt_size = 0,
                               group_by = "sample",
                               split_by = "strain",
                               colors = c("white", "grey50"),
                               errorbar_size = 10,
                               errorbar_color = "black",
                               title_size = 14,
                               axis_title_y_size = 12,
                               legend_position = "none",
                               title = F,
                               nrow = 1,  
                               p_adjust_method="bonferroni"){
  
  # Prepare list objects of plot and stats
  p_list <- vector("list", length=length(cells)) ; names(p_list) <- cells
  stats_list <- vector("list", length=length(cells)) ; names(stats_list) <- cells
  
  for(i in seq_along(cells)){
    # plot for each cell type
    p_list[[i]] <- VlnPlot(object, idents = cells[i], features = feature, pt.size=pt_size, group.by = group_by, split.by = split_by, cols = colors)
    p_list[[i]] <- p_list[[i]] + stat_summary(fun = mean, geom='point', size = errorbar_size, colour = errorbar_color, shape=95)
    p_list[[i]] <- p_list[[i]] + ggtitle(cells[i]) + theme(plot.title = element_text(size = title_size), axis.title.x = element_blank(), axis.title.y = element_text(size = axis_title_y_size), legend.position = legend_position)
    p_list[[i]] <- p_list[[i]] + scale_x_discrete(limits=xaxis)
    
    # stats for each cell type
    data <- object@meta.data[WhichCells(object, idents = cells[i]),]
    if(is.element(feature, colnames(object@meta.data))){
      ## if feature is included in the colnames(object@meta.data) 
      stats_list[[i]] <- stats::pairwise.wilcox.test(x=data[[feature]], g=data$stim, paired=F, p.adjust.method=p_adjust_method)
      p_list[[i]] <- p_list[[i]] + ylab(feature)
    } else {
      ## if feature is NOT included in the colnames = gene or ADT feature
      expression <- object@assays$RNA@data[feature,][rownames(data)]
      stats_list[[i]] <- stats::pairwise.wilcox.test(x=expression, g=data$stim, paired=F, p.adjust.method=p_adjust_method)
      p_list[[i]] <- p_list[[i]] + ylab(feature)
    }
  }
  
  # Title for wrap_plots or not
  if(title==T){
    p_list <- p_list %>% lapply(function(x){ x + theme(axis.title.y=element_blank()) })
    plots <- patchwork::wrap_plots(p_list, nrow = nrow) + patchwork::plot_annotation(title=feature)
  } else { 
    plots <- patchwork::wrap_plots(p_list, nrow = nrow)
  }
 
  return(list(plots, stats_list))
}
```

```{r}
VlnPlot(MCAOall, idents="Ly6ChiMo_all", features = "Cd300lb", group.by = "stim", split.by = "strain", slot = "scale.data") + stat_summary(fun = mean, geom='point', size = 15, colour = "red", shape=95) + scale_x_discrete(limits=c("N.flox","N.LMcreflox","MO1h.flox","MO1h.LMcreflox","MO3h.flox","MO3h.LMcreflox"))
```

```{r}
Idents(MCAOall) <- MCAOall$final.celltype_forScoring
VlnPlot_with_stats(MCAOall,
                   cells = c("Ly6ChiMo_all","Neut"),
                   feature = "Cd300a",
                   xaxis=c("N.flox","N.LMcreflox","MO1h.flox","MO1h.LMcreflox","MO3h.flox","MO3h.LMcreflox"),
                   group_by = "stim",
                   split_by = "strain")
```


```{r}
Idents(MCAOall) <- MCAOall$final.celltype_forScoring
VlnPlot_with_stats(MCAOall,
                   cells = c("Ly6ChiMo_all","Neut"),
                   feature = "Cd300lb",
                   xaxis=c("N.flox","N.LMcreflox","MO1h.flox","MO1h.LMcreflox","MO3h.flox","MO3h.LMcreflox"),
                   group_by = "stim",
                   split_by = "strain")
```


```{r}
Idents(MCAOall) <- MCAOall$final.celltype_forScoring
VlnPlot_with_stats(MCAOall,
                   cells = c("Ly6ChiMo_all","Microglia"),
                   feature = "Cd300a",
                   xaxis=c("N.flox","N.LMcreflox","MO1h.flox","MO1h.LMcreflox","MO3h.flox","MO3h.LMcreflox"),
                   group_by = "stim",
                   split_by = "strain")
```


```{r}
Idents(MCAOall) <- MCAOall$final.celltype_forScoring
VlnPlot_with_stats(MCAOall,
                   cells = c("Ly6ChiMo_all","Microglia"),
                   feature = "Cd300lb",
                   xaxis=c("N.flox","N.LMcreflox","MO1h.flox","MO1h.LMcreflox","MO3h.flox","MO3h.LMcreflox"),
                   group_by = "stim",
                   split_by = "strain")
```

```{r}
DimPlot(MCAOall, label = T)
```


```{r}
FeaturePlot(MCAOall, features = "Cd300lb", max.cutoff = "q80")
```










-----------------------------------------------------------------------------------------------------------

```{r}
library(fgsea)
library(data.table)
library(ggplot2)
library(tidyverse)

# Extract gene list from "after FindMarkers DEG data"
# If genes are non-human genes, convert to human genes using "biomaRt" -> convert=T (default is convert=F) 
# All duplicated genes are removed

FindMarkers_to_Humangenelist <- function(DEG, pval_adj, convert=F) {
  Data <- DEG %>% rownames_to_column(var="Gene")
  Data <- Data %>% filter(p_val_adj <= pval_adj) %>% dplyr::select(Gene, avg_logFC)
  Data$avg_logFC <- exp(Data$avg_logFC)
  List <- Data$avg_logFC
  names(List) <- Data$Gene
  
  if (convert) {
    require("biomaRt")
    human = useMart("ensembl", dataset = "hsapiens_gene_ensembl")
    mouse = useMart("ensembl", dataset = "mmusculus_gene_ensembl")
    
    genesV2 = getLDS(attributes = c("mgi_symbol"), filters = "mgi_symbol", values = names(List), mart = mouse, attributesL = c("hgnc_symbol"), martL = human, uniqueRows=F)
    
    
    # Remove duplicates in both mouse and human
    mouse_dupli_pos <- whichall(genesV2$MGI.symbol[duplicated(genesV2$MGI.symbol)], genesV2$MGI.symbol)
    human_dupli_pos <- whichall(genesV2$HGNC.symbol[duplicated(genesV2$HGNC.symbol)], genesV2$HGNC.symbol)
    dupli_pos <- c(mouse_dupli_pos, human_dupli_pos) %>% unique()
    
    genesV2 <- genesV2[-dupli_pos,]
    List <- List[genesV2$MGI.symbol]
    names(List) <- genesV2$HGNC.symbol
  } else {}
  
  return(List)
}

gene_list <- FindMarkers_to_Humangenelist(Ly6ChiMo_1h_DEGs, pval_adj = 0.1, convert = F)

EfferoPathway_GSEA <- vector("list", length=2)
names(EfferoPathway_GSEA) <- c("Effero_UP","Effero_DOWN")
EfferoPathway_GSEA[["Effero_UP"]] <- Effero.UP
EfferoPathway_GSEA[["Effero_DOWN"]] <- Effero.DOWN

fgseaRes <- fgsea(pathways = EfferoPathway_GSEA, 
                  stats    = gene_list,
                  minSize  = 15,
                  maxSize  = 500,
                  nperm = 1000) %>% as.tibble()
fgseaRes

plotEnrichment(EfferoPathway_GSEA[["Effero_UP"]], gene_list) + labs(title="Effero_UP")
plotEnrichment(EfferoPathway_GSEA[["Effero_DOWN"]], gene_list) + labs(title="Effero_DOWN")
```









```{r}
VlnPlot(MCAOall, idents = "Tcell", features = "Tcf7", group.by = "stim") + stat_summary(fun.y = mean, geom='point', size = 15, colour = "black", shape=95) + theme(legend.position="none", axis.title.x = element_blank())
```

```{r}
FeaturePlot(MCAOall, features = "Cxcr4", max.cutoff = "q70")
```


```{r}
Ly6ChiMo_1h_GSEA <- Ly6ChiMo_1h_DEGs %>% rownames_to_column(var="NAME")
Ly6ChiMo_1h_GSEA <- Ly6ChiMo_1h_GSEA %>% filter(p_val_adj <= 0.1) %>% dplyr::select(NAME, avg_logFC)
Ly6ChiMo_1h_GSEA <- data.frame(NAME=Ly6ChiMo_1h_GSEA$NAME, Description="na", flox=1, LMcreflox=exp(Ly6ChiMo_1h_GSEA$avg_logFC), stringsAsFactors = F)
Ly6ChiMo_1h_GSEA <- Ly6ChiMo_1h_GSEA %>% filter(NAME != "Lyz2") %>% filter(NAME != "Cd300a")
Ly6ChiMo_1h_GSEA

write.csv(Ly6ChiMo_1h_GSEA, file="/Users/kazumasa/Desktop/Dry_analysis/kkd9_Tcell_Stroke/GSEA/Ly6ChiMo_1h_GSEA.csv")
```


